Sparse Word Embeddings for Multi-domain Machine Translation

### 2019-05-10 2019/emnlp/sparse.tex
new
rewrite table 5

\section{Introduction \label{sec:introduction}}
\fyDone{Merge refs and order chronologically}
\fyTodo{Homogeneize cite keys, avoid arxiv}

Despite fast developpement thanks to new architectures \cite{Kalchbrenner13recurrent, Sutskever2014Sequence, bahdanau2014neural, Vaswani17attention}, Machine Translation (MT) still struggles with data scarcity. Domain adaptation, or it's special case Multi-domain, is the situation where in-domain data (such as banking) is rare while out-domain data such as news are plenty, one aims to leverage out-domain data to improve quality of Machine Translation system which is perfectible while being trained with only the in-domain dataset. Traditionally, ones train a generic model using a very large corpora then use in-domain dataset to fine-tune the model. It is ubiquitous that the bias to the in-domain dataset used in fine-tuning makes model worse in translating other domains, thus that we have not been able to fine-tune a model to several domains at once. This phenomenon can be implied by well-known problem in Machine Learning, Catastrophic Interference \cite{McCloskey1989Catastrophic}. When there is a shift in the distribution of training data, standard backpropagation neural network\fyTodo{Generic ? backprop or NN problem ?} gradually lose information learned from other domains while learning only target domain.

In \fyTodostar{Specify DA}{Multi-domain Machine Translation}, ones have to deal with polysemies whose meaning can be totally different in different domains, for example, the word "chair" means an household tool in "if you are taking a medicine which may cause low blood pressure when rising from a chair or bed " (extracted from medical corpus EMEA \cite{Tiedemann2009RANLP5}) while the word "chair" means to preside over a meeting in following sentence "The President of the ECB or , in his absence , the Vice-President , chairs the meetings of the Governing Council , the Executive Board and the General Council of the ECB. " (extracted from European Central Bank corpora \cite{Tiedemann2009RANLP5}). Using context information is not sufficient to differ these polysemies. Therefore using the same word embedding for polysemies obstructs the model from differentiating the meaning of a polysemy in one domain from it's other meaning in the other domain.
\begin{table}[h]
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|}
\hline
English Words & French translation & Domain \\ \hline
security & titre financier & Financial \\
security & s\'ecuti\'e & IT\\
\hline
joint & articulaire & medical\\
joint & conjoint & banking\\
\hline
chair & chaise & general \\
chair & pr\'esider, pr\'esident & banking \\
\hline
\end{tabular}
}
\caption{Polysemies}
\label{table:polysemy}
\end{table}

\begin{table}[h]
\resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||}
\hline
English sentence & French translation & Corpus \\ 
\hline
"Flu-like" symptoms such as headaches, \colorbox{red}{joint} pains, feelings of weakness, dizziness, and tiredness may occur, especially at the start of treatment. & Des symptômes grippaux tels que céphalées, douleurs \colorbox{red}{articulaires}, sensation de faiblesse, vertige et asthénie, peuvent survenir, en particulier en début de traitement. & EMEA \\
\hline
In my opinion, Mr President, this \colorbox{red}{joint} debate fully bears this out. & Cette discussion \colorbox{red}{commune} en est, Monsieur le Président, la preuve vivante. & EPPS \\
\hline
The increasing number of central banks using the same IT platform for their own purposes has provided unique opportunities to undertake \colorbox{red}{joint} projects , exploit synergies and better manage the relationship with the vendor. & Le nombre croissant de banques centrales utilisant la même plate-forme informatique pour leurs besoins propres a offert des occasions uniques de lancer des projets \colorbox{red}{communs}, d'exploiter des synergies et de mieux gérer les relations avec le fournisseur. & ECB \\
\hline
\end{tabularx}
}
\caption{Translation}
\label{table:polysemy}
\end{table}
\fyTodo{Typical plan: the problems, existing solutions and their limits, our idea and contributions}
In this work, we present a new design for word embedding that is composed of different regions which are activate and deactivate corresponding to domains. 
\\ To evaluate, we use 3 corpora of 3 different domains: Medical, Banking and Administration and 2 different architectures: Transformer and Attentional recurrent network. The test sets are selectioned from shared task each domains and two other general test sets such as news commentary and IWSLT. The reader could find more details in Experimetal section \ref{subsec:data}
\fyTodo{More precise: two architectures, two languages pairs, multiple domains, also improves generic}

@@

\subsection{Problem statement}
\fyTodo{Use math for notation, label equations and such}
\begin{definition}{Domain}
\label{def:domain}
A domain is probabilistic distribution of translation $(x,y)$ in a given corpora. Given corpora $C$, we denote $D(C)$ the domain of $C$.
\end{definition}
\fyTodo{We need more: the source, the target, etc}
In machine translation, the loss function for training is:
\begin{equation}
\begin{split}
E_{(x,y) \sim p_{rel}}[-log(p_{\theta}(y|x))] &= \\
= E_{x \sim p_{rel}(x)}[KL(p_{rel}(y|x) & \mid p_{\theta}(y|x))] + \\
+ E_{x \sim p_{rel}} &[H(p_{rel}(y|x))]
\end{split}
\end{equation}.

@@

In this equation, the domain is $p_{rel}(x,y)$. One aims to approximate to model to target domain $p_{rel}$. The more the domain of training data close to the domain of test set, the better performance it could achieve over test set.\\
In the training of a generic model, the $p_{rel}$ is oftenly a general domain, noted $p_{gen}$ which is defined by a set of several corpora which belongs to different topics (e.g medical, banking, adminstration). Therefore the generic model is not usually good enough for translating by topic in which one is more interested. In order to specialize the model, one usually finetunes generic model by continue the traing from $\theta^*$, which was optimized on general domain, with corpora of the interested topic. However, there is always a dramatical shift from generic domain $p_{gen}$ to specialization domain $p_{spec}$, that usually leads to catastrophic forgetting in neural network using backpropagation \cite{McCloskey1989Catastrophic}. The finetuned model has lower performance in translating sentences, which are more related to other topic, than generic model. Indeed, the translation $(x,y)$ could be very different in different topic. For instance, in financial document, to translate "security" into "titre financier" is more likely than to translate it into "securit\'e" but in IT document. Therefore, the shift from general domain containing these two corpora to one of them is not negligible. \\
In order to conduct the model translating by a certain topic, we might use conditional probability conditioned by the given topic $p(y|x,d)$. Given a set of training corpora, we assume that there are a limited d engendering topic, i.e, there are d corpora $C_i$ $i \in [1,..,d]$ representing d topical domains $D(C_i)$ respectively. We are then interested in approximating $p(y,x|i)$ for $i \in [1,..,d]$ and use $p(y|x,i)$ for the inference in topic $i$. From now, we formalize the multi-domain problem for machine translation in following equation

@@

\theta^* = \argmin_{\theta} E_{(x,y) \sim D(C_{i})} [-log & (p_{\theta}(y|x,i))] \; \forall i \in [1..d]

@@

A trivial solution for this equation is $\theta^* = (\theta^*_{0},...,\theta^*_{d})$ and $p_{(\theta_{0},...,\theta_d)}(y|x,i)$ is independent of $\theta_{j}$ $\forall j \neq i$, i.e, $\exists f:\Omega_i \times C(D_i) \rightarrow [0,1]: f_{\theta_i}(y,x) = p_{(\theta_{0},...,\theta_d)}(y|x,i)$ where $\Omega_i$ is set of all possible values of $\theta_i$. \\
The model above is not different than ensemble of $d$ models specialized for one domain. However, we could mitigate this seperation by using shared paramaters denoted $\theta_s$ then reformulate the model as following: \\

@@

where $\Omega_i$ is set of all possible values of $\theta_i$ and $\Omega_s$ is set of all possible values of $\theta_s$. \\
However, there is a problem that the couple $\theta_s^*$ and $\theta_i^*$ have to be optimal $\forall i \in [1..d]$.\\

@@

then optimize each $\theta_i$ (as additional factor used for fine-tuning the model to the domain $D(C_{i})$) the perplexity with respect to true distribution of domain
\theta^*_{i} = \displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
Our first approach to multi-domain machine translation is to build such trivial solution in calibrating positions and sizes of domain paramters $\theta_i$ and shared parameters $\theta_s$ inside one architecture.
\subsection{Sparse word embedding}
\label{sec:sparse}
This section explains a new design for word embedding used in multi-domain model. As mentioned above, we separate parameter set into $D+1$ parameter sets correspond to D domains and one shared paramater set. Our first attempt is to split standard vector word embedding into $D+1$ regions named $\theta_i$ for $i \in [1,..,D]$ and $\theta_s$.
\begin{figure}[h]
\center
    \includegraphics[width=0.8\linewidth]{Sparse1}
    \caption{Sparse word embeddings. The red region contains units that are activated only when an input from the corresponding domain is presented; the other (green) regions are deactivated; the blue (generic) region is always activated.} 
    \label{fig:network}
  \end{figure}
\fyTodo{Explain vanishing ?}
Figure~\ref{fig:network} presents our proposed design. During backprogation, the \fyTodo{fix notation}{projection matrix $P$} receives vanishing gradient at regions corresponding to deactivated regions in the word embedding. Those regions are also vanished in forward step, thus do not interfere the training on the domain to which they do not correspond.

@@

\subsection{Domains and data \label{ssec:data}}
To evaluate the performance of proposed architecture, we design experiments in which we want to train an NMT for 3 domains such as medical, administrative documents and business briefly denoted by EMEA, EPPS, ECB according to training corpora name respectively. We use 3 corpora for training: European Medicines Agency; European Central Bank and European Parliament \cite{Tiedemann2009RANLP5}. We randomly split those 3 corpora into training, validation and test set with size described in table \ref{table:Corpora}. We use validation sets for choosing the best model according to the average BLEU score on 3 validation sets. We also realize that the test sets origined from same corpora as training sets are likely easy for trained model, thus can not provide fair evaluation. Therefore, we we use Khresmoi-test; newstest2009 and test2007 for domains: EMEA, EPPS. Unfortunately, we could not find any official test sets for ECB domain. We also want to evaluate the generalization of trained model. The model is also required to achieve comparable performance to generic model. To do so, we use newstest 2009 and IWSLT 2010 whose contain does not particularly belong to any domain.\fyTodo{Clarify / simplify text}

\begin{table}[H]
\fyTodo{Too small ! Use abbrevs (En, Fr, ECB, EMEA, EPPS)}
  \resizebox{\columnwidth}{!}{
\begin{tabular}{ |l|l|l|l|l|l| }
\hline
Task & Corpora & Train & Dev & Test & Vocabulary \\ \hline
\multirow{5}{*}{$En \rightarrow Fr$} & European Medicines Agency & 1090568 & 1000 & 1000 & English: 30164, French: 30398\\
 & European Central Bank & 191960 & 1000 & 1000 &\\
 & European Parliament & 2005723 & 1000 & 1000 & \\ \hline
\multirow{5}{*}{$En \rightarrow Ge$} & European Medicines Agency & 1108752 & 1000 & 1000 & English: 30159, German: 30698\\
 & European Central Bank & 111174 & 1000 & 1000 &\\
 & European Parliament & 1920209 & 1000 & 1000 & \\ \hline
\hline
\end{tabular}
}
\caption{Corpora }
\label{table:Corpora}
\end{table}
\subsection{Baselines \label{ssec:baselines}}
\fyTodo{Describe baselines}

\subsection{NMT model configuration}
We evaluate our method on two state-of-the-art encoder-decoder architectures: a recurrent architecture based on attentional birectional Long Short-Term Memory (LSTM) cells and the Transformer architecture of \citet{Vaswani17attention}.
More precisely, for the Transformer we use the same settings as described in \cite{Vaswani17attention}. For the recurrent architecture, in order to fairly compare to the work of \citet{Zeng18multidomain}, we use a standard configuration with one layer bidirectional LSTM with a encoder hidden size of 1024; one attentional unidirectional LSTM layer with same hidden size in decoder; and word embeddings of size 512. The implementation can be found in OpenNMT-tf \cite{Klein2017OpenNMT}.
\fyTodo{Language pairs, BPE number, optimizer}
\fyTodo{Motivate the split - discuss experimentally embedding size}
For the implementation of sparse embeddings, we split the vector embedding of size 512 into four regions $[8,8,8,488]$, corresponding respectively to EMEA, EPPS, ECB domain and generic region. If sentence comes from domain $i$, regions for domains $j,\forall j \neq i$ will be masked as 0. We then use a dense layer of size 512 to fuse the active domain region and the generic region.

@@

Each iteration of algorithm \ref{algo:1}, the batch is doubled because it contains 2 types of word embedding for each sentence (using only generic region; using generic region and active domain region). The reason to do this is to minimize simultaneously both losses \\
$\theta^*_{s}=\displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i}=\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$ 
We admit that this is not the optimal way. However, this procedure makes training very simple.\fyTodo{Explain technicalities - future work ?}

We also take in account the problem of overfitting that could occur for small corpora. Indeed, real data are not always balanced for every domain. For instance, in our experiments, the size of corpora are very different where EPPS is largest with approximately 2 millions sentences, EMEA contains about 1 million sentences and ECB is the smallest with only 200 000 sentences for English French and 100 000 for English-German. If we train each corpora with same number of batches, ECB will be trained too oftenly, that easily leads to overfitting. Therefore, we perform backpropagation on corpora with frequencies according to sizes of corpora. \fyTodo{Refs on this ? or contrast ?}

\subsection{Results}
\begin{table}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 28.56 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.64 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 &  & 11.1 \\
 \hline
 ECB-finetuned & 9.2 & 18.39 & 55.45 & 12.13 & 16.12 & 8.71 &  & 7.19 \\
 \hline
 Sparse(1) & 70.45 & 38.23 & 54.69 & 34.66 & 31.24 & 21.36 & 28.12 & 26.02 \\
 \hline
 Sparse(2) & 69.91 & 38.05 & 54.2 & 35.22 & 31.25 & 21.36 & 28.12 & 26.02 \\
 \hline
 Sparse(3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 &  & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{BPE-detokenized BLEU score for English-French with the Transformer architecture. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by a pre-trained domain classififer}
\label{tab:1}
\end{table}

\begin{table}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 64.57 & 26.47 & 68.67 & 21.77 & 23.50 & 13.9 & 17.04 & 18.85 \\
 \hline
 EMEA-finetuned & & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse(1) & 70.55 & 26.17 & 68.07 & 21.50 & 23.30 & 14.05 & 16.64 & 19.04\\
 \hline
 Sparse(2) & 70.67 & 26.24 & 66.97 & & & 14.05 & 16.64 & 19.04 \\
 \hline
 Domain Control & & & & & & & & \\
 \hline
\end{tabularx}}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. Notations are same as Table~\ref{tab:1}}
\label{tab:2}
\end{table}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned  & & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse (1) & 68.51 & 35.75 & 51.19 & 28.88 & 28.92 & 17.89 & 22.73 & 21.08 \\
 \hline
 Sparse (2) & & & & & & & & \\
 \hline
 Domain Control & & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{Zeng18multidomain} use Bidirectional-LSTM}
\label{tab:3}
\end{figure}

>>>>

@@

\subsection{Problem statement}
\fyTodo{Use math for notation, label equations and such}
\begin{definition}{Domain}
\label{def:domain}
A domain is probabilistic distribution of translation $(x,y)$ in a given corpora. Given corpora $C$, we denote $D(C)$ the domain of $C$.
\end{definition}
\fyTodo{We need more: the source, the target, etc}
In machine translation, the loss function for training is:
\begin{equation}\label{eq:1}
\begin{split}
E_{(x,y) \sim p_{rel}}[-log(p_{\theta}(y|x))] &= \\
= E_{x \sim p_{rel}(x)}[KL(p_{rel}(y|x) & \mid p_{\theta}(y|x))] + \\
+ E_{x \sim p_{rel}} &[H(p_{rel}(y|x))]
\end{split}
\end{equation}.

@@

In this equation, the domain is $p_{rel}(x,y)$. In minimizing given objective \ref{eq:1}, one aims to approximate the objective domain $p_{rel}$. In inference, provided the model was trained on certain training data, the more likely test set is generated from domain of training data, the better performance.\\
In general, a generic model is trained first with a mix of several corpora which belongs to different topics (e.g medical, banking, adminstration) whose the domain $p_{rel}$ is considered as a general domain, noted $p_{gen}$. Being trained with a general mixed corpora, the generic model is not usually good enough for translating by topic. In order to improve topical translation quality, specializing generic model is required. One usually finetunes the generic model by continue the training from initial value $\theta^*$, which was optimized on general domain, using corpora of interested topic. However, there is always a dramatical shift from generic domain $p_{gen}$ to specialization domain $p_{spec}$. Indeed, the translation $(x,y)$ could be very different in different topic. For instance, in financial document, to translate "security" into "titre financier" is more likely than to translate it into "securit\'e" but in IT document. Therefore, the shift from general domain containing these two corpora to one of them is not negligible. This shift usually leads to catastrophic forgetting in neural network using backpropagation \cite{McCloskey1989Catastrophic}. In effect, the finetuned model usually shows lower performance in translating sentences, which are less related to the finetuning topic, than generic model. 
In order to conduct the model translating topic by topic, we might refer to conditional probability conditioned by topic $p(y|x,d)$. Given a set of training corpora, we assume that there are a limited d engendering topic, i.e, there are d corpora $C_i$ $i \in [1,..,d]$ representing d topical domains $D(C_i)$ respectively. We are then interested in approximating $p(y,x|i)$ for $i \in [1,..,d]$ and use $p(y|x,i)$ for the inference in topic $i$. From now, we formalize the multi-domain problem for machine translation in following equation
\begin{equation} \label{eq:2}

@@

\theta^* = \argmin_{\theta} \displaystyle{\mathop{\sum}_{i \in [1..d]}} E_{(x,y) \sim D(C_{i})}[-log(p_{\theta}(y|x,i))]

@@

It is obvious that
\begin{equation} \label{eq:3}
\argmin_{\theta} \displaystyle{\mathop{\sum}_{i \in [1..d]}} E_{(x,y) \sim D(C_{i})} &[-log(p_{\theta}(y|x,i))] \\
\geq \displaystyle{\mathop{\sum}_{i \in [1..d]}} \argmin_{\theta} E_{(x,y) \sim D(C_{i})} &[-log(p_{\theta}(y|x,i))]
A trivial solution for the equation \ref{eq:2} is $\theta^* = (\theta^*_{0},...,\theta^*_{d})$ and $p_{(\theta_{0},...,\theta_d)}(y|x,i)$ is independent of $\theta_{j}$ $\forall j \neq i$, i.e, $\exists f:\Omega_i \times C(D_i) \rightarrow [0,1]: f_{\theta_i}(y,x) = p_{(\theta_{0},...,\theta_d)}(y|x,i)$ where $\Omega_i$ is set of all possible values of $\theta_i$. \\
The trivial solution is not rather than ensemble of $d$ models specialized for one domain. However, we could reduce the seperation by using shared paramaters denoted $\theta_s$ then reformulate the model as following: \\

@@

where $\Omega_i$ is set of all possible values of $\theta_i$ and $\Omega_s$ is set of all possible values of $\theta_s$. The optimization problem will become
\displaystyle{\mathop{\sum}_{i \in [1..d]}} \argmin_{\theta_{0},...,\theta_{d}, \theta_s} E_{(x,y) \sim D(C_{i})} [-log(p_{\theta_s,\theta_i}(y|x,i))]
However, the couple $\theta_s^*$ and $\theta_i^*$ are hardly optimal $\forall i \in [1..d]$.\\

@@

then optimize each $\theta_i$ (as additional factor used for fine-tuning the model to the domain $D(C_{i})$) the perplexity with respect to true distribution of domain
\begin{equation}
\theta^*_{i} = \displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
\end{equation} 
Our first approach to multi-domain machine translation is to build such trivial solution in calibrating positions and sizes of domain paramters $\theta_i$ and shared parameters $\theta_s$ inside one architecture.
\subsection{Sparse word embedding}
\label{sec:sparse}
This section explains a new design for word embedding used in multi-domain model. As mentioned above, we separate parameter set into $D+1$ parameter sets correspond to D domains and one shared paramater set. Our first attempt is to split standard vector word embedding into $D+1$ regions named $\theta_i$ for $i \in [1,..,D]$ and $\theta_s$.
\begin{figure}[h]
\center
    \includegraphics[width=0.8\linewidth]{Sparse1}
    \caption{Sparse word embeddings. The red region contains units that are activated only when an input from the corresponding domain is presented; the other (green) regions are deactivated; the blue (generic) region is always activated.} 
    \label{fig:network}
  \end{figure}
\fyTodo{Explain vanishing ?}
Figure~\ref{fig:network} presents our proposed design. During backprogation, the \fyTodo{fix notation}{projection matrix $P$} receives vanishing gradient at regions corresponding to deactivated regions in the word embedding. Those regions are also vanished in forward step, thus do not interfere the training on the domain to which they do not correspond.

@@

\subsection{Domains and data \label{ssec:data}}
In our experiments, there are 3 domains such as medical, administrative documents and business briefly denoted by EMEA, EPPS, ECB according to training corpora name respectively and 2 language pairs: English-French, English-German. We use 3 corpora for training: European Medicines Agency; European Central Bank and European Parliament \cite{Tiedemann2009RANLP5}. We randomly split those 3 corpora into training, validation and test set with size described in table \ref{table:Corpora}. We use validation sets for choosing the best model according to the average BLEU score on 3 validation sets. We also realize that the test sets origined from same corpora as training sets are likely easy for trained model, thus can not provide fair evaluation. Therefore, we we use Khresmoi-test; newstest2009 and test2007 for domains: EMEA, EPPS. Unfortunately, we could not find any official test sets for ECB domain. We also want to evaluate the generalization of trained model. The model is also required to achieve comparable performance to generic model. To do so, we use newstest 2009 and IWSLT 2010 whose contain does not particularly belong to any domain. \fyTodo{Clarify / simplify text}
\begin{table*}
  \begin{tabular}{ |l|l|l|l|l|l| }
\hline
Task & Corpora & Train & Dev & Test & Vocabulary \\ \hline
\multirow{5}{*}{$En \rightarrow Fr$} & EMEA & 1090568 & 1000 & 1000 & English: 30164, French: 30398\\
 & ECB & 191960 & 1000 & 1000 &\\
 & EPPS & 2005723 & 1000 & 1000 & \\ \hline
\multirow{5}{*}{$En \rightarrow Ge$} & EMEA & 1108752 & 1000 & 1000 & English: 30159, German: 30698\\
 & ECB & 111174 & 1000 & 1000 &\\
 & EPPS & 1920209 & 1000 & 1000 & \\ \hline
\hline
\end{tabular}
\caption{Corpora }
\label{table:Corpora}
\end{table*}
To reduce size of vocabulary, we apply Byte-Pair Encoding with 30000 merge operations, then select approximately 30000 frequent words to build vocabulary for each language. 
\subsection{Baselines \label{ssec:baselines}}
To validate our findings, we compared sparse embedding model with standard models using State-of-the-Art Transformer \cite{Vaswani17attention} architecture and Attention Recurrent Neural Network architecture. Our baselines consist of generic models trained with mixed corpora (denoted mixed in the table of scores); models finetuned to each domain using 15000 iterations over in-domain data (denoted $+ft_{EMEA}$, $+ft_{EPPS}$, $+ft_{ECB}$ in the table of scores); models using Domain features of \cite{Kobus17domaincontrol} (noted DC in the table of scores) and multi-domain model proposed by \cite{Zeng18multidomain} (denoted WDCMT in the table of scores). \\
For all of models, we set size of word embedding equal to 512; size of hidden layers equal to 1024 for Recurrent Neural Network and 512 for Transformer. 
\begin{itemize}
	\item Transformer: size of word embedding: 512; size of hidden layers: 512; size of inner feed forward layer: 2048; Multi-head: 8; number of layers: 6.
	\item Attention Recurrent Neural Network: Bidirection LSTM encoder, unidirectional LSTM decoder, Luong Attention Mechanism, size of word embedding: 512; size of hidden layers: 1024; number of layers: 1
	\item DC: size of domain embedding:2 ; same settings for both architecture: Transformer and Attention Recurrent Neural Network.
	\item WDCMT: Bidirection Gated recurrent units (denoted GRU) encoder, unidirectional conditional GRU decoder, size of word embedding: 512; size of hidden layers: 1024; size of domain layers: 300; number of layers: 1
\end{itemize}
The implementation can be found in OpenNMT-tf\cite{Klein2017OpenNMT} and \url{https://github.com/DeepLearnXMU/WDCNMT}
\subsection{Sparse NMT model configuration}
\fyTodo{Motivate the split - discuss experimentally embedding size}
For the implementation of sparse embeddings, we split the vector embedding of size 512 into four regions with size $[8,8,8,488]$ for instance, the choice will be dicussed in \ref{secc:region_size}. If sentence comes from domain $i$, regions for domains $j,\forall j \neq i$ will be masked as 0 while generic region is always activated. We then use a dense layer of size 512 to fuse the active domain region and the generic region.

@@

Each iteration of algorithm \ref{algo:1}, the batch contains 2 types of word embedding for each sentence: using only generic region; using generic region and present domain region. The reason to do this is to minimize simultaneously both losses: \\
$\theta^*_{s}=\displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i}=\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$ 
We admit that this is not the optimal way. However, this procedure makes training very simple. \fyTodo{Explain technicalities - future work ?}

We also take into account the problem of overfitting that could occur for small corpora. Indeed, real data are not always balanced for every domain. For instance, in our experiments, the size of corpora are very different where EPPS is largest with approximately 2 millions sentences, EMEA contains about 1 million sentences and ECB is the smallest with only 200 000 sentences for English French and 100 000 for English-German. If we train each corpora with same number of batches, ECB will be trained too oftenly, that easily leads to overfitting. Therefore, we select batches from each corpora with frequencies proportional to its size. \fyTodo{Refs on this ? or contrast ?}

\subsection{Results}
\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 28.56 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.64 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 &  & 11.1 \\
 \hline
 ECB-finetuned & 26.93 & 27.09 & 56.52 & 22.04 & 22.92 & 12.94 & 17.51 & 13.99 \\
 \hline
 Sparse(1) & 74.26 & 37.67 & 54.07 & 33.85 & 30.86 & 20.97 & 28.11 & 25.70 \\
 \hline
 Sparse(2) & 73.97 & 37.81 & 53.67 & 34.17 & 30.93 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse(3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 &  & & \\
 \hline
\end{tabularx}
\end{center}

\caption{BPE-detokenized BLEU score for English-French with the Transformer architecture. Sparse(1) uses correponding domain tag for EMEA, EPPS, ECB test sets and generic tag for newstest and IWSLT. Sparse(2) uses generic tag for all of test sets. Sparse(3) uses tag predicted by a pre-trained domain classififer}
\label{tab:1}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 64.57 & 26.47 & 68.67 & 21.77 & 23.50 & 13.9 & 17.04 & 18.85 \\
 \hline
 EMEA-finetuned & 68.35 & 17.02 & 32.87 & 21.15 & 15.94 & 8.92 & 11.21 & 13.49 \\
 \hline
 EPPS-finetuned & 36.19 & 26.29 & 40.71 & 19.67 & 23.69 & 14.08 & 16.47 & 19.24 \\
 \hline
 ECB-finetuned & 24.72 & 18.36 & 74.05 & 11.31 & 16.64 & 9.11 & 10.8 & 11.0 \\
 \hline
 Sparse(1) & 70.9 & 26.30 & 68.9 & 21.42 & 23.73 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse(2) & 70.86 & 26.14 & 68.59 & 21.95 & 23.79 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 63.48 & 26.27 & 66.95 & 21.45 & 23.95 & & & \\
 \hline
\end{tabularx}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. Notations are same as Table~\ref{tab:1}}
\label{tab:2}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned  & 72.06 & 18.62 & 16.78 & 25.88 & 13.38 & 9.26 & 10.94 & 5.73 \\
 \hline
 EPPS-finetuned & 35.47 & 34.61 & 39.56 & 27.11 & 28.8 & 17.3 & 21.85 & 20.61 \\
 \hline
 ECB-finetuned & 21.93 & 22.6 & 51.53 & 14.74 & 20.23 & 9.74 & 12.10 & 10.47 \\
 \hline
 Sparse (1) & 71.73 & 35.21 & 50.91 & 29.62 & 29.05 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (2) & 70.59 & 35.22 & 49.68 & 29.51 & 29.32 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 68.26 & 35.13 & 50.09 & 27.86 & 29.34 & & & \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{Zeng18multidomain} use Bidirectional-LSTM}
\label{tab:3}
\end{table*}
